A weighted data representation based approach for manifold learning

### 2018-11-05 DimReduction/Lle/Documentation/Article_lle.tex
Adding implementation section to Lle documentation

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

@@

    Whith these tools the linear combinations of neighbors can be expressed as

@@

\cite{matlab}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{algorithm2e}

@@

    With these tools the linear combinations of neighbors can be expressed as

@@

For the implementation of the method the programing language MATLAB \cite{matlab}
was used. This tool is specifically desing for matrix operations, which makes it
an appropriate option to address the problem in an easy way.

The Algorithm \ref{alg1} shows the seudo-code to compute a low
dimentional representation of a multidimensional manifold that is represented as
a matrix of points called data of dimensions $n$x$d$.

\begin{algorithm}
    $n$ = number of points\\
    $p$ = output dimensions\\
    $k$ = number of neighbors\\
    \vspace{0.5cm}
    $W$ = zeros($n$)\\
    \For{i in 1:n}{
        $x_i$ = data($i$)\\
        $k_i$ = get\_nearest\_neighbors($x_i$, $k$)\\
        $V_i$ = data($k_i$)\\
        $G$ = $(x_i e^t - V_i)^t (x_i e^t - V_i)$\\
        solve($G w_i = e$)\\
        $W(i)$ = $w_i$ / sum($w_i$)
    }
    \vspace{0.5cm}
    $M$ = $(I-W) * (I-W)^t$\\
    $V$ = get\_eigenvectors($M$)\\
    $Y$ = select\_smaller($p$, $V$)

    \vspace{0.5cm}

    \caption{Computation of low dimensional representation}
    \label{alg1}
\end{algorithm}
